---
title: "Journal club homework"
author: "Roberta Vasconcellos"
date: "07/03/2021"
output: html_document
---

```{r iris}
summary(iris)
head(iris)
```

---
title: "ggplot2 examples and exercises"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document contains all the code that is displayed during the workshop. The
document is an RMarkdown document which means that it can be compiled, along 
with the code chunks thus executing and capturing the output of the code within
the document. To read more about RMarkdown see the website for the package, as
well as the [Get Started](https://rmarkdown.rstudio.com/lesson-1.html) guide.

### Exercises
While it is encouraged to follow along in this document as the workshop 
progresses and execute the code to see the result, an important part is also to
experiment and play, thus learning how the different settings affect the output.

The document will contain code chunks with the code examples discussed during 
the talk, but it will also contain chunks intended for completing small 
exercises. These will use the examples as a starting point and ask you to modify
the code to achieve a given output. Completing these are optional, but highly 
recommended, either during or after the workshop.

### Dependencies
This document comes with a list of required packages. 

```{r, echo=FALSE}
packages <- c(
  'ggplot2',
  'ggrepel',
  'patchwork',
  'ggraph',
  'dplyr',
  'gganimate',
  'gifski',
  'ggforce',
  'ggthemes',
  'maps',
  'sf',
  'tidyr',
  'concaveman',
  'remotes'
)
# Uncomment the next lines (remove the first #) to install the packages
# install.packages(packages)
# remotes::install_github("hrbrmstr/hrbrthemes")
# Load standard packages
library(ggplot2)
```

### Datasets
We will use an assortment of datasets throughout the document. The purpose is 
mostly to showcase different plots, and less on getting some divine insight into
the world. While not necessary we will call `data(<dataset>)` before using a new
dataset to indicate the introduction of a new dataset.

## Introduction
We will look at the basic ggplot2 use using the faithful dataset, giving 
information on the eruption pattern of the Old Faithful geyser in Yellowstone
National Park.

```{r}
data("faithful")
# Basic scatterplot
ggplot(data = faithful, 
       mapping = aes(x = eruptions, y = waiting)) + 
  geom_point()
# Data and mapping can be given both as global (in ggplot()) or per layer
ggplot() + 
  geom_point(mapping = aes(x = eruptions, y = waiting),
             data = faithful)
```

If an aesthetic is linked to data it is put into `aes()`

```{r}
ggplot(faithful) + 
  geom_point(aes(x = eruptions, y = waiting, colour = eruptions < 3))
```

